On the uniqueness and stability of dictionaries \\ for sparse representation of noisy signals

### 2019-05-10 manuscripts/IEEE/final_submission.tex
final fina

We hope that these remaining challenges pique the interest of the community in picking up where we have left off and that the theoretical tools we have showcased here may be of use to this end.

>>>>

We hope these remaining challenges pique the interest of the community to pick up where we have left off and that the theoretical tools showcased here may be of use to this end.
